### 2021-04-21 input/proposal.tex
combine Sec III and IV - try 1

\section{Scoped broadcast}
\label{sec:scoped}

Scoped broadcast is a communication primitive that propagates a
message around its broadcaster within an application-dependant scope.
For instance, a \process from Paris could scoped broadcast messages to
all \processes in Paris; and \processes from other cities would never
deliver such messages.
Scoped broadcast only targets a connected \emph{subset} of \processes
in the whole distributed system.
%
Distributed systems such as Edge infrastructures comprise
heterogeneous machines interconnected by communication
links. \Processes may crash but are not byzantine.

% \TODO{dynamic graph: superscript with $t$?}

@@

\Processes can reliably communicate through asynchronous message
passing to other known \processes called neighbors. Using epidemic
propagation (or gossiping), \processes can reliably broadcast messages
by forwarding delivered messages from neighbors to
neighbors~\cite{birman1999bimodal, hadzilacos1994modular,
  nedelec2018causal, raynal2013distributed}. However, uniform reliable
broadcast states that \emph{all} correct \processes must deliver all
broadcast messages. This proves costly in large scale systems
comprising thousands of \processes. Instead, we define \emph{scoped
broadcast} where messages reach only an application-dependant subset
of connected \processes, thus significantly reducing the generated
traffic of broadcast.

@@

This definition encompasses more specific definitions of related
work~\cite{hsiao2005scoped, lue2006scoped, wang2015prodiluvian}.  This
definition also highlights that epidemic propagation and scoped
broadcast have well-aligned preoccupations: It highlights the
transitive relevance of messages, thus \processes can stop forwarding
messages as soon as the corresponding predicate becomes unverified.
For instance, a \process from Paris could scoped broadcast messages to
all \processes in Paris. This requires \processes to store and
maintain their city location in their local state. \Processes stop
delivering and forwarding their received messages when they come from
a different city.  In another instance, a \process from Paris could
scoped broadcast messages to all \processes in Paris plus neighboring
cities. This requires \processes to overload forwarded messages the
first time they reach another city. The predicate checks if messages
already reached two distinct cities before delivery. Similarly to
uniform reliable broadcast, scoped broadcast implementations expose
different trade-offs on space, time, and communication.

Next Section introduces an adaptive scoped broadcast where the state
of each \process is dynamic and changes depending on all distinct
scopes that exist in the system.

In this section, we propose to dynamically adapt the scopes of \NAMEB
using \NAMEB itself for the sake of efficiency: a \NAMEB message may
modify the state of a \process, consequently changing predicate
evaluations over deliveries.  At any time, a \process decides whether
or not it becomes the center (or \emph{source}) of a scope (or
\emph{partition}). \Processes must eventually rally the partition
corresponding to their closest source despite concurrent operations,
and dynamic changes in the network.

\noindent In that regard, we introduce \NAME (stands for
\underline{A}daptive \underline{S}coped broad\underline{cast}), a
wait-free reactive protocol for dynamic logical partitioning that
enables adaptive scoped broadcast in dynamic distributed
systems. \NAME's operation guarantees that \processes eventually reach
consistent partitioning by efficiently propagating their state
changes. \NAME's overhead actually depends on its operations and
current partitions in the system. When the system becomes quiescent,
\processes eventually converge to their respective partition and do not
require further communication afterward.

\noindent This section starts by introducing consistent partitioning
and its implementation when a \process can only become a new source to
create a new partition, i.e., it cannot revoke its self-appointed
status of source. Then, it extends to include the latter behavior: it
introduces the properties that guarantee consistent partitioning in
such context, and it details our implementation called \NAME along
with its complexity analysis.

>>>>

%% In this section, we propose to dynamically adapt the scopes of \NAMEB
%% using \NAMEB itself for the sake of efficiency: a \NAMEB message may
%% modify the state of a \process, consequently changing predicate
%% evaluations over deliveries.  At any time, a \process decides whether
%% or not it becomes the center (or \emph{source}) of a scope (or
%% \emph{partition}). \Processes must eventually rally the partition
%% corresponding to their closest source despite concurrent operations,
%% and dynamic changes in the network.

%% \noindent In that regard, we introduce \NAME (stands for
%% \underline{A}daptive \underline{S}coped broad\underline{cast}), a
%% wait-free reactive protocol for dynamic logical partitioning that
%% enables adaptive scoped broadcast in dynamic distributed
%% systems. \NAME's operation guarantees that \processes eventually reach
%% consistent partitioning by efficiently propagating their state
%% changes. \NAME's overhead actually depends on its operations and
%% current partitions in the system. When the system becomes quiescent,
%% \processes eventually converge to their respective partition and do not
%% require further communication afterward.

%% \noindent This section starts by introducing consistent partitioning
%% and its implementation when a \process can only become a new source to
%% create a new partition, i.e., it cannot revoke its self-appointed
%% status of source. Then, it extends to include the latter behavior: it
%% introduces the properties that guarantee consistent partitioning in
%% such context, and it details our implementation called \NAME along
%% with its complexity analysis.

To assign and maintain \processes to their best partition according to
replica creations/removals as well as dynamic infrastructure changes,
we designed and implemented \NAME (\NAME stands for
\underline{A}daptive \underline{S}coped broad\underline{cast}).  \NAME
relies on a primitive that allows a \process to broadcast a message
within a limited scope.  This primitive is used in a first algorithm
to deliver consistent partitioning each time \process creates a new
replica within the system. This algorithm is then extended to include
replica removals as well as dynamic changes of the infrastructure.
This section discussed the different properties that guarantee
consistent partitioning in such a context and details the \NAME
implementation along with its complexity analysis.

\subsection{Scoped broadcast}
\label{subsec:scoped}

%For instance, a \process from Paris could scoped broadcast messages to
%all \processes in Paris; and \processes from other cities would never
%deliver such messages.
%Scoped broadcast only targets a connected \emph{subset} of \processes
%in the whole distributed system.
%

% \TODO{dynamic graph: superscript with $t$?}
In the edge infrastructure we consider, nodes are heterogeneous and
interconnected by communication links. \Processes involved in the
management of the data sets may crash but are not byzantine.  Finally,
\processes can reliably communicate through asynchronous message
passing to other known \processes called neighbors.
A more formal definition of our system is given below:

@@

%Using epidemic
%propagation (or gossiping), \processes can reliably broadcast messages
%by forwarding delivered messages from neighbors to
%neighbors~\cite{birman1999bimodal, hadzilacos1994modular,
%  nedelec2018causal, raynal2013distributed}.
%
%However, uniform reliable
%broadcast states that \emph{all} correct \processes must deliver all
%broadcast messages. This proves costly in large scale systems
%comprising thousands of \processes. Instead, we define \emph{scoped
%broadcast} where messages reach only an application-dependant subset
%of connected \processes, thus significantly reducing the generated
%traffic of broadcast.

We define the Scoped broadcast (\NAMEB) as a communication primitive that propagates a
message around its broadcaster within an application-dependant scope :

@@

This definition encompasses more specific definitions of related
work~\cite{hsiao2005scoped, lue2006scoped, wang2015prodiluvian}.  It
also highlights that epidemic propagation and scoped broadcast have
well-aligned preoccupations. More precisely, it underlines the transitive relevance of
messages, thus \processes can stop forwarding messages as soon as the
corresponding predicate becomes unverified.
%For instance, a \process
%from Paris could scoped broadcast messages to all \processes in
%Paris. This requires \processes to store and maintain their city
%location in their local state. \Processes stop delivering and
%forwarding their received messages when they come from a different
%city.  In another instance, a \process from Paris could scoped
%broadcast messages to all \processes in Paris plus neighboring
%cities. This requires \processes to overload forwarded messages the
%first time they reach another city. The predicate checks if messages
%already reached two distinct cities before delivery. Similarly to
%uniform reliable broadcast, scoped broadcast implementations expose
%different trade-offs on space, time, and communication.

\NAMEB is used to change the state of each \process dynamically, depending on all partitions that exist in the system.
